Robust co-occurrence quantification for low-dimensional lexical distributional semantics

### 2016-02-29 paper.tex

We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting); as well as the best scores reported by \cite{TACL570}, and those given by word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:simlex-ppmi-best-simlex}.

>>>>

We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting); as well as the best scores reported by \cite{TACL570}, and those given by word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex}.
